---
title: "A-SA23204193-2023-09-25"
author: "SA23204193"
date: "2023-09-25"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-SA23204193-2023-09-25}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Question

• Proof that what value $ρ =\frac{l}{d}$ should take to minimize the asymptotic variance of $\hat\pi$? (m ∼ B(n, p),
using δ method)

• Take three different values of ρ (0 ≤ ρ ≤ 1, including $ρ_{min}$) and use Monte Carlo simulation to verify
your answer. ($n = 10^6$, Number of repeated simulations K = 100)



### Ex 5.6

In Example 5.7 the control variate approach was illustrated for Monte Carlo integration of $$\theta=\int_0^1e^xdx.$$

Now consider the antithetic variate approach. Compute $Cov(e^U, e^{1−U})$ and
$Var(e^U + e^{1−U})$, where U ∼ Uniform(0,1). What is the percent reduction in
variance of θˆ that can be achieved using antithetic variates (compared with
simple MC)?

### Ex 5.7

Refer to Exercise 5.6. Use a Monte Carlo simulation to estimate θ by the
antithetic variate approach and by the simple Monte Carlo method. Compute
an empirical estimate of the percent reduction in variance using the antithetic
variate. Compare the result with the theoretical value from Exercise 5.6.

## Answer

### 1.

一次投针相交概率: $p=\frac{2l}{d\pi}$

设投针$n$次中有$m$次相交，记$X_n=\frac{m}{n}$, 则由$m\thicksim B(n,p)$,

有$X_n$的渐近分布服从$N(p,\frac{p(1-p)}{n})$, $\sqrt n (X_n-p) \thicksim N(0, p(1-p))$;

$\hat \pi = \frac{2l}{dX_n}$, 令$g(x)=\frac{2l}{dx}$, 则$g^\prime(x)=-\frac{2l}{dx^2}$

由$\delta$ method, $\sqrt n (\hat \pi - \frac{2l}{dp}) = \sqrt n (\frac{2l}{dX_n} - \frac{2l}{dp}) = \sqrt n (g(X_n)-g(p)) \thicksim N(0, (g\prime(p))^2 p(1-p))$

其中$(g\prime(p))^2 p(1-p) = \frac{4l^2}{d^2 p^4}p(1-p) = \pi^2(\frac{\pi d}{2l}-1)$

由于$0 \le l \le d$, 可知$l = d$, 即$\rho = 1$时，$\hat \pi$的渐近方差最小. 

$\rho$分别取值为0.6, 0.8, 1, 其中$\rho_{min} = 1$.

```{r}
K = 100
pihat <- rep(0, K)
for (i in 1:K) {
  set.seed(i)
l <- 0.5
d <- 1
n <- 1e6
X <- runif(n,0,d/2)
Y <- runif(n,0,pi/2)
pihat[i] <- 2*l/d/mean(l/2*sin(Y)>X)
}
var(pihat)

```

```{r}
pihat <- rep(0, K)
for (i in 1:K) {
  set.seed(i+100)
l <- 0.8
d <- 1
n <- 1e6
X <- runif(n,0,d/2)
Y <- runif(n,0,pi/2)
pihat[i] <- 2*l/d/mean(l/2*sin(Y)>X)
}
var(pihat)
```

```{r}
pihat <- rep(0, K)
for (i in 1:K) {
  set.seed(i+200)
l <- 1
d <- 1
n <- 1e6
X <- runif(n,0,d/2)
Y <- runif(n,0,pi/2)
pihat[i] <- 2*l/d/mean(l/2*sin(Y)>X)
}
var(pihat)
```
可见$\rho_{min} = 1$时估计有最小的方差. 

### Ex 5.6

$Cov(e^U, e^{1-U}) = \mathrm Ee - \mathrm Ee^U \mathrm Ee^{1-U} = -e^2+3e-1$

$\mathrm {Var}(e^U+e^{1-U}) = \mathrm{Var}e^U + \mathrm{Var}e^{1-U} + 2\mathrm{Cov}(e^U, e^{1-U}) = -3e^2+10e-5$

$\mathrm{Var}\hat\theta = \mathrm{Var}(\frac{1}{m}\sum_{j=1}^{m/2}(e^U+e^{1-U})) = \frac{1}{m^2}\frac{m}{2}\mathrm{Var}(e^U+e^{1-U}) = \frac{1}{2m}(-3e^2+10e-5) = \frac{0.0078}{m}$

```{r}
(-3*exp(2)+10*exp(1)-5)/2
```

while the variance of the simple MC estimator is 0.2420/m, 
```{r}
(0.2420-0.0078)/0.2420
```
using antithetic variates, variance decreased by 96.8%.

### Ex 5.7

```{r}
m <- 100000
K <- 100
est1 <- rep(0,K)
est2 <- rep(0,K)

set.seed(3)
for (i in 1:K) {
  U <- runif(m)
  T1 <- exp(U) #simple MC
  T2 <- (exp(U) + exp(1-U))/2
  est1[i] <- mean(T1)
  est2[i] <- mean(T2)
}
var(est1)
var(est2)
1-var(est2)/var(est1)
```
方差减小比例的模拟结果为97.8%, 与Ex 5.6中理论计算结果96.8%相接近. 

