---
title: "Homework-2023.09.18"
author: "SA23204193"
date: "2023-09-23"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Homework-2023.09.18}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Question

利用逆变换法实现sample在replace=TRUE时的功能. 
Exercises 3.2, 3.7, 3.9, 3.10 (pages 94-96, Statistical Computing with R).

## Answer

```{r}
library("knitr")
library("kableExtra")
library("ggplot2")
library("rmarkdown") 
library("dplyr")

```

```{r}
my.sample <- function(x, size, prob = NULL){
  # x: vector
  # 放回抽样
  l <- length(x)
  
  inversefunc <- function(u){
    return(x[ceiling(u*l)])
  }
  
  u <- runif(size)
  x <- inversefunc(u)
  
  return(x)
}
my.sample(c(1,3,5,7,9,11,13,15,17,19), 50)
```


### Ex 3.2
standard Laplace distribution, pdf: 
$f(x) = \frac{1}{2}e^{-|x|} = \begin{cases} \frac{1}{2}e^{x}, & x \le 0 , \\ \frac{1}{2}e^{-x}, & x \gt 0, \end{cases}$
cdf:
$F(x) = \begin{cases} \frac{1}{2}e^{x}, & x \le 0 , \\ 1-\frac{1}{2}e^{-x}, & x \gt 0, \end{cases}$

$F^{-1}(x) = \begin{cases} \log(2x), & 0 \lt x \le \frac{1}{2} , \\ -\log(2-2x), &\frac{1}{2} \lt x \lt 1, \end{cases}$

```{r}
u <- runif(1000)
x <- rep(0, 1000)
Laplace <- function(x){
  y=x
  for (i in 1:length(x)) {
    if(x[i]<0) y[i]=1/2*exp(x[i])
    else y[i]=1/2*exp(-x[i])
  }
  
  return(y)
}
for (i in 1:1000) {
  if(u[i] < 1/2)
    x[i] = log(2*u[i])
  else
    x[i] = -log(2-2*u[i])
}
hist(x, prob = TRUE)
y <- seq(-6, 6, 0.01)
lines(y, Laplace(y))

```

### Ex 3.7

$\rm{Beta}(a, b)$ distribution, 
pdf: $f(x)=\frac {\Gamma (\alpha +\beta )}{\Gamma (\alpha )\Gamma (\beta )}x^{\alpha -1}(1-x)^{\beta -1}$



```{r}
my.beta <- function(a, b, n){
  j=k=0
  y <- numeric(n)
  while (k < n) {
    u <- runif(1)
    j <- j + 1
    x <- runif(1) 
    if (x^(a-1) * (1-x)^(b-1) > u) {
      k <- k + 1
      y[k] <- x
    }
  }
return(y)
}
y <- my.beta(3,2,1000)
hist(y, prob = T)
z <- seq(0, 1, 0.005)
lines(z,  12* z^(3-1) * (1-z)^(2-1))
```


### Ex 3.9

```{r}
my.epan <- function(n){
  x <- rep(0, n)
  for (i in 1:n) {
    u1 <- runif(1, -1, 1)
    u2 <- runif(1, -1, 1)
    u3 <- runif(1, -1, 1)
    if(abs(u3)>=abs(u2)&&abs(u3)>=abs(u1)) x[i] <- u2
    else x[i] <- u3
  }
  return(x)
}
x <- my.epan(1000)
hist(x, prob = TRUE)
```

### Ex 3.10

Proof:

$(U_1, U_2, U_3)$服从$[-1,1]\times[-1,1]\times[-1,1]$上的均匀分布, 
$P(X\le x)=P(U_2\le x||U_3|\ge|U_2| and |U_3|\ge|U_1|) P(|U_3|\ge|U_2| and |U_3|\ge|U_1|) + P(U_3\le x||U_3|\lt|U_2| or |U_3|\lt|U_1|) P(|U_3|\ge|U_2| and |U_3|\ge|U_1|)$ 
其中$P(|U_3|\ge|U_2| and |U_3|\ge|U_1|)=P(|U_3|=max\{|U_1|,|U_2|,|U_3|\})=\frac{1}{3}$

$P(U_3\le x||U_3|\lt|U_2| or |U_3|\lt|U_1|)=\frac{2}{3}$

$\{|U_3|\ge|U_2| and |U_3|\ge|U_1|\}$在$(U_1, U_2, U_3)$分布范围内的体积为$\frac{1}{3}\times2\times2\times2=\frac{8}{3}$, $\{|U_3|\lt|U_2| or |U_3|\lt|U_1|\}$ 的对应体积为$2^3-\frac{8}{3}=\frac{16}{3}$.

$P(U_2\le x||U_3|\ge|U_2| and |U_3|\ge|U_1|) = 1-\frac{\frac{5}{6}x^3-\frac{3}{2}x^2-\frac{3}{2}x+\frac{5}{6}}{8/3}$

$P(U_3\le x||U_3|\lt|U_2| or |U_3|\lt|U_1|) = 1-\frac{(1-x)^2+\frac{1}{3}x^3-x+\frac{2}{3}}{16/3}$

cdf: $F(x)=P(X\le x) = \frac{1}{3} \times (1-\frac{\frac{5}{6}x^3-\frac{3}{2}x^2-\frac{3}{2}x+\frac{5}{6}}{8/3}) + \frac{2}{3} \times 1-\frac{(1-x)^2+\frac{1}{3}x^3-x+\frac{2}{3}}{16/3}$

pdf: $f(x) = F'(x) = \frac{3}{4}(1-x^2)$
即为Epanechnikov kernel.


